\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, total={7in, 9in}]{geometry}\usepackage{titlesec}
\usepackage{ragged2e}

% format section headers
\titleformat{\section}
  {\normalfont\fontsize{14}{16}\bfseries}{\thesection}{1em}{}
 
% define new commands
\newcommand{\name}[1]{\begin{center}\LARGE\textbf{#1}\end{center}}
\newcommand{\newitem}[2]{\item \textbf{ #1 \hfill #2}\\}

% document
\begin{document}
\name{Patrick Varin}
\justify
\section*{Mission}
My goal is to bring state of the art robotics research to consumer and industrial applications by designing efficient algorithms for robust control and estimation.

\section*{Education}
\begin{itemize}
\newitem{Harvard University: Doctoral Candidate}{2016-Present}
Degree: Candidate for Ph.D. in Computer Science\\
GPA: 3.83

\newitem{Franklin W. Olin College of Engineering}{2010-2014}
Degree: B.S. Engineering with a concentration in Robotics\\
GPA: 3.80

\end{itemize}
\section*{Experience}
\begin{itemize}
\newitem{Facebook: Product Manager}{2014-2016}
I have led a number of teams ranging in size from 5 to 17 that have included engineering, design, marketing and analytics. My responsibilities include product vision, building roadmaps, and coordination.

\newitem{Olin College of Engineering: Teacher's Assistant}{2011-2014}
I have been a teachers assistant for courses such as \emph{Modeling and Control of the Physical World}, \emph{Linear Algebra}, \emph{Differential Equations}, \emph{Partial Differential Equations}, \emph{Signals and Systems}, and \emph{Robotics}. My responsibilities included giving supplemental lectures, grading papers, holding office hours, and designing exams.

\newitem{University of Notre Dame: Research in Medical Robotics}{Summer 2013}
On a team of two, I worked towards developing a hyper-realistic robotic manikin capable of speech and facial expression. This manikin is intended for used in medical training.

\newitem{University of Minnesota: Research in Dynamics of Pattern Formation}{Summer 2012}
On a team of four, I conducted research on the dynamics of pattern formation in a model of chemotaxis. I developed the numerical tools that we used to discover a previously unrecorded behavior. Our results are published in the SIAM Undergraduate Research Journal.
\end{itemize}

\section*{Publications}
\begin{itemize}
\newitem{Invasion Fronts and Pattern Formation in a Model of Chemotaxis in One and Two Dimensions}{}
SIAM Undergraduate Research Online (2013)

\end{itemize}

\section*{Notable Projects}
\begin{itemize}
\newitem{Senior Capstone in Engineering}{2013-2014}
Led a team of five Olin seniors in partnership with Analogic Corp to develop signal processing techniques for single photon counting in high energy X-Ray technology for application in medial and security imaging.

\newitem{SAE Baja: Electrical Team Leader}{2013-2014}
I recruited and led a team of 12 undergraduate electrical and computer engineering students to design and build the software and sensor suite for an off-road vehicle. This data was critical in the design of the car as well as providing the driver with real time 
\end{itemize}
\end{document}
