\documentclass{article}
\usepackage[utf8]{inputenc}


\usepackage[a4paper, total={6.5in, 9in}]{geometry}

% remove page numbering
\pagestyle{empty}

% format section headers
\usepackage{titlesec}
\titleformat{\section}{\normalfont\fontsize{14}{16}\bfseries}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{16pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% format lists to remove space and use dash bullets
\usepackage{enumitem}
\setlist{nosep}
\renewcommand\labelitemi{--}

% define new commands
\newcommand{\name}[1]{\begin{center}\huge\textbf{#1}\end{center}\vspace{2em}}
\newcommand{\personal}[4]{
	\noindent#1\hfill#3\\
	#2\hfill#4
}
%\newcommand{\personal}[4]{
%	\moveleft.5\hoffset\centerline{#1}
%	\moveleft.5\hoffset\centerline{#2}
%	\moveleft.5\hoffset\centerline{#3}
%	\moveleft.5\hoffset\centerline{#4}
%}
\newcommand{\newitem}[2]{\noindent\textbf{#1 \hfill #2}\\}
\newcommand{\gimmespace}{\vspace{1em}}

% document
\begin{document}
\name{Patrick Varin}
\personal{38 2nd Street}{Cambridge, MA 02141}{(262) 844-0294}{patrickjvarin@gmail.com}
\section*{Mission}
\noindent My goal is to bring state-of-the-art robotics research to consumer and industrial applications by designing efficient algorithms for robust control, state estimation, and filtering.

\section*{Education}
\newitem{Harvard University}{2016-Present}
Computer Science Ph.D Student\\
2017 Smith Fellow\\
GPA: 3.83
\gimmespace

\newitem{Franklin W. Olin College of Engineering}{2010-2014}
B.S. Engineering with a concentration in Robotics\\
GPA: 3.80

\section*{Experience}

\newitem{Harvard Agile Robotics Lab: PhD Researcher}{2016-Present}
I am conducting research on algorithms for control and estimation in the presence of rigid body contact. Specifically I am interested in applications such as robot locomotion and manipulation.
\gimmespace

\newitem{Facebook: Product Manager}{2014-2016}
I led teams of 8-17 engineers, marketers, designers, and data analysts at Facebook.
\begin{itemize}
\item We built the machine learning backend for notifications resulting in 10\% increase in click-through rate for push notifications and 40\% increase in click-through rate for email notifications.
\item We grew Facebook commerce groups--now larger than Craigslist--part of Facebook's core strategy.
\item We re-architected Facebook NewsFeed, increasing engagement on low performance Android phones by 30\%.
\end{itemize}
\gimmespace

\newitem{Olin College of Engineering: Teacher's Assistant}{2011-2014}
I have been a teacher's assistant for courses such as \emph{Modeling and Control of the Physical World}, \emph{Linear Algebra}, \emph{Differential Equations}, \emph{Partial Differential Equations}, \emph{Signals and Systems}, and \emph{Robotics}. My responsibilities included giving supplemental lectures, grading papers, holding office hours, and designing exams.
\gimmespace

\newitem{University of Notre Dame: Research in Medical Robotics}{Summer 2013}
I worked on a team developing a hyper-realistic robotic mannequin capable of speech and facial expression, intended for use in medical training. I was personally responsible for the software and electronics.
\gimmespace

\newitem{University of Minnesota: Research in Dynamics of Pattern Formation}{Summer 2012}
On a team of four, I conducted research on the dynamics of pattern formation in a model of chemotaxis. I developed the numerical tools that we used to discover a previously unrecorded behavior. Our results are published in the Society of Industrial and Applied Mathematics (SIAM) Undergraduate Research Journal.

\section*{Publications}
\newitem{Invasion Fronts and Pattern Formation in a Model of Chemotaxis in One and Two Dimensions}{}
Bose, K., Cox, T., Silvestri, S., and Varin, P. (2013). Invasion fronts and pattern formation in a model of chemotaxis in one and two dimensions. SIAM Undergrad. Res. Online, 6, 228-245.

\section*{Notable Projects}
\newitem{Senior Capstone in Engineering: Project Manager}{2013-2014}
I led a team of five Olin seniors in partnership with Analogic Corp. to develop signal processing techniques for single photon counting in high energy X-ray technology for application in medical and security imaging.
\gimmespace

\newitem{Baja Society of Automotive Engineers: Electrical Team Leader}{2013-2014}
I recruited and led a team of 12 undergraduate electrical and computer engineering students to design and build the software and sensor suite for an off-road vehicle. This data was critical in the design of the car as well as providing the driver with real time diagnostics.
\end{document}
